The Expected Place of the Local Group in the Cosmic Web

### 2014-08-12 paper/main.tex
final version + possible alignment conflict

\begin{abstract}
We explore the characteristics of the Local Group (LG)
location in the cosmic web using a cosmological simulation in the
$\Lambda$CDM cosmology.  
We use the Hessian of the gravitational potential to classify regions
on scales of $\sim 2$ Mpc as a peak, sheet, filament or void.  
The LG is represented by two samples of halo
pairs. 
The first is a general sample composed by pairs with
similar masses and isolation criteria as observed in the LG.  
The second is a subset with additional kinematic constaints also
constrained by observations. 
We find that the pairs in the LG sample with all constraints are: (i)
preferentially   located in filaments and sheets, (ii) located in in a
narrow range of local overdensity $0<\delta<2$, web ellipticity $0.1<e<1.0$ and
prolateness $-0.4<p<0.4$.  (iii) strongly aligned with the cosmic web,
in particular for pairs in filaments/sheets the pair orbital angular
momentum tends to be perpendicular to the filament direction or the
sheet plane.
A stronger alignment is present for the vector linking the two halos,
which lies along the filament or the sheet plane.  
We show that the first and second results are expected trends with the LG
total mass. 
However, the strong alignments with the cosmic web cannot be explained
by a simple mass dependency. 
Additionally, we fail to find a strong correlation of the spin of each
halo in the pair with the cosmic web.
This precise characterization of the expected place of the LG in the
cosmic web in a $\Lambda$CDM cosmology opens the door to a detailed
understanding of diverse features characterizing the Milky Way and the
Andromeda galaxies.

@@

\subsection{Web Overdensity, Ellipticity and Anisotropy}

@@

There are two important features in Figure \ref{fig:alignment_n}.
First the alignments themselves. 
There is a strong anti-alignment signature between $\hat{n}$ and the
third eigenvector. 
With respect to the second eigenvector the distribution is consistent
with no aligment. 
For the first eigenvector there is a strong alignment, an expected
result after considering the results with the other eigenvectors and
keeping in mind that the eigenvectors are orthonormal.
Second, the alignment strenght changes for the different samples. 
For the anti-alignment with $\hat{e}_3$ the signal strenghtens as we
move from the GS to the 3$\sigma$ into the 2$\sigma$ sample.

Quantitatively, the anti-alignment feature found with the $\hat{e}_3$ 
vector means that for 2$\sigma$ sample, $\sim 50\%$ pairs have
$|\mu|<0.2$ ($78$ degrees angle), and $\sim 75\%$ pairs have $|\mu|<0.4$
($66$ degrees angle). 
These signals do not change significantly on
different environments as has been already show in different alignment
studies that similar \citep{Libeskind2013} or identical
\citep{ForeroRomero2014} web finding techniques as ours.
In particular  these trends hold for pairs in filaments and walls.
If we consider only pairs in filaments, we have that the pair orbital
angular momentum tends to be perpendicular to the filament direction,
in the case of sheets it tends to lie perpendicular to the sheet plane.

Can the increase of the alignment strenght in the different samples be
explained as a consequence of different mass dependencies as the
results in the previous section? No. 
In Figure \ref{fig:median_alignment_n} we show the median of
$\mu\equiv\hat{e}_i\cdot\hat{n}$ in different total mass bins.
Lines show the median $\mu$-mass relation for the three 
eigenvectors in the GS, Dots represent the results for the
2$\sigma$-3$\sigma$ samples. 
In a mass range around $1.5-2.0 \times 10^{12}$ \msun the median of
$\mu$ decreases as we increase the constraints on the pairs, not as a
result of narrowing mass selection.

@@

We also find a stronger signal as we move into more restrictive
samples, although the signal from the GS is already very
significant. 
Quantitatively, the alignment feature with $\hat{e}_3$
means that for the 2$\sigma$ and 3$\sigma$ samples, $\sim 50\%$ pairs
have $|\mu|>0.8$ ($36$ degrees angle) and $\sim 25\%$ pairs have
$|\mu|<0.95$ ($18$ degrees angle).

Considering that the 2$\sigma$ and 3$\sigma$ samples move primarely
along the radial direction, we can say that the motion of the LG
halos is mostly done along the $\hat{e}_3$ vectors, consistent with
recent results that report a strong alignment of halo's peculiar
velocities along that direction \citep{ForeroRomero2014}.

@@

In the LG, the angle between MW and M31 spin is $\sim60^{\circ}$
($|\mu|=0.5$) and the angles between spins and orbital angular
momentum are $\sim33^{\circ}$ ($|\mu|=0.83$) and $\sim76^{\circ}$
($|\mu|=0.24$) for MW and M31 respectively
\citep{2012ApJ...753....9V}. Consistent with our results of no particular
alignement.

@@

The mass range of the LG pairs is tightly correlated with the
properties of the web where they reside as shown in Table
\ref{table:web_type} and Figure \ref{fig:median_fraction}. Recent
analytical \citep{Alonso2014} and numerical studies \citep{Metuki2014}
have shown that the local overdensity is the dominant web property
that define the abundance and properties of halos. Quantities derived
from the tidal tensor play a secondary role.

Therefore, in our case, the fact that the preferred LG total mass is
around $1-4\times 12^{12}$\Msun implies that the preferred environment
are filaments and sheets with an overdensity close to the average
value, with values for the ellipticity and prolateness also correlated
with the overdensity.

However, there are alignment signals with the cosmic web that are not
mass dependent and seem to be stronger for different LG samples. There
is a clear anti-alignment between the third eigenvector and the
orbital angular momentum vector, meaning that this vector is
perpendicular to filaments and the sheets, depending on the
particular web environment. We also found that the vector joining the
LG halos are aligned with the third eigenvector; i.e. the pair is
aligned with the filaments and lies on the sheets.

@@

\section*{Acknowledgements}
REG was supported by Proyecto Financiamiento Basal PFB-06 'Centro de Astronomia y Tecnologias Afines' and Proyecto Comit\'e Mixto ESO 3312-013-82.
The Geryon cluster at the Centro de Astro-Ingenieria UC was extensively used for the calculations performed in this paper. The Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided funding for several improvements to the Geryon cluster.

>>>>

\begin{abstract}
We explore the characteristics of the Local Group (LG)
location in the cosmic web using a cosmological simulation in the
$\Lambda$CDM cosmology.  
We use the Hessian of the gravitational potential to classify regions
on scales of $\sim 2$ Mpc as a peak, sheet, filament or void.  
The LG is represented by two samples of halo
pairs. 
The first is a general sample composed by pairs with
similar masses and isolation criteria as observed in the LG.  
The second is a subset with additional kinematic constaints also
constrained by observations. 
We find that the pairs in the LG sample with all constraints are: (i)
preferentially   located in filaments and sheets, (ii) located in in a
narrow range of local overdensity $0<\delta<2$, web ellipticity $0.1<e<1.0$ and
prolateness $-0.4<p<0.4$.  (iii) strongly aligned with the cosmic web,
in particular for pairs in filaments/sheets the pair orbital angular
momentum tends to be perpendicular to the filament direction or the
sheet plane.
A stronger alignment is present for the vector linking the two halos,
which lies along the filament or the sheet plane.  
We show that the first and second results are expected trends with the LG
total mass. 
However, the strong alignments with the cosmic web cannot be explained
by a simple mass dependency. 
Additionally, we fail to find a strong correlation of the spin of each
halo in the pair with the cosmic web.
Applied to the observed LG, there is a potential conflict between
these alignments and recent claims of an universal subhalo accretion
direction. 
This highlights the relevance of achieving a precise characterization
of the place of the LG in the cosmic web in a the cosmological context
provided by $\Lambda$CDM.

@@

\subsection{Web Overdensity, Ellipticity and Prolateness}

@@

There are two important features in Figure \ref{fig:alignment_n}.
First the alignments themselves. 
There is a strong anti-alignment signature between $\hat{n}$ and the
third eigenvector. 
With respect to the second eigenvector the distribution is consistent
with no aligment. 
While for the first eigenvector there is a strong alignment, an expected
result considering the results with the other eigenvectors and
keeping in mind that they are orthonormal.
Second, the alignment strenght changes for the different samples. 
For the anti-alignment with $\hat{e}_3$ the signal strenghtens as we
move from the GS to the 3$\sigma$ into the 2$\sigma$ sample.

Quantitatively, the anti-alignment feature found with the $\hat{e}_3$ 
vector means that for 2$\sigma$ sample, $\sim 50\%$ pairs have
$|\mu|<0.2$ ($>78$ degrees angle), and $\sim 75\%$ pairs have $|\mu|<0.4$
($>66$ degrees angle). 
These signals do not change significantly on
different environments as has been already show in different alignment
studies with similar \citep{Libeskind2013} or identical
\citep{ForeroRomero2014} web finding techniques as ours.
In particular these trends hold for pairs in filaments and walls.
If we consider only pairs in filaments, we have that the pair orbital
angular momentum tends to be perpendicular to the filament direction,
in the case of sheets it tends to lie perpendicular to the sheet plane.

Can the increase of the alignment strenght in the different samples be
explained as a consequence of different mass dependencies as the
results in the previous section? No. 
In Figure \ref{fig:median_alignment_n} we show the median of
$\mu\equiv\hat{e}_i\cdot\hat{n}$ in different mass bins.
Lines show the median $\mu$-mass relation for the three 
eigenvectors in the GS, dots represent the results for the
2$\sigma$-3$\sigma$ samples. 
Around the total mass $1.5-2.0 \times 10^{12}$ \msun in the RS
samples, the median of $\mu$ decreases as we tighten constraints
on the pairs, but not as a result of the narrowing mass selection.

@@

We also find a stronger signal as we move into more restrictive
samples, although the signal from the GS is already very
significant. 
Quantitatively, the alignment feature with $\hat{e}_3$
means that for the 2$\sigma$ and 3$\sigma$ samples, $\sim 50\%$ pairs
have $|\mu|>0.8$ ($<36$ degrees angle) and $\sim 25\%$ pairs have
$|\mu|>0.95$ ($<18$ degrees angle). Similar to the previous case of
the $\hat{n}$ vector, the increasing strenght of the
$\hat{r}$ alignment cannot be explained by a selection on mass.

Considering that the 2$\sigma$ and 3$\sigma$ samples correspond to
pairs moving along the radial direction, we can say that the
motion of the LG halos is mostly done along the $\hat{e}_3$
vectors. This is consistent with recent results that report a strong
alignment of halo's peculiar velocities along that direction
\citep{ForeroRomero2014}.

@@

In the LG, the angle between MW and M31 spin is $\sim60^{\circ}$
($|\mu|=0.5$) and the angles between spins and orbital angular
momentum are $\sim33^{\circ}$ ($|\mu|=0.83$) and $\sim76^{\circ}$
($|\mu|=0.24$) for MW and M31 respectively
\citep{2012ApJ...753....9V}. 
Consistent with our results of no strong alignement.

@@

The mass range of the LG pairs is tightly correlated with the
properties of the web where they reside as shown in Table
\ref{table:web_type} and Figure \ref{fig:median_fraction}. Recent
analytical \citep{Alonso2014} and numerical studies \citep{Metuki2014}
have shown that the local overdensity is the dominant web property
that define the abundance and properties of halos. Other quantities
derived from the tidal tensor play a secondary role defining
properties such as its formation history.

In our case, the fact that the preferred LG total mass is around
$1-4\times 12^{12}$\Msun implies that the preferred environment are
filaments and sheets with an overdensity close to the average
value. 
Correspondignly, the values for the ellipticity and prolateness are
also well defined for the LG pairs given its correlation with the
total mass.

We conclude that the typical LG environment and its characteristics is
a robust results depending mostly on the LG total mass.

However, the alignments with the cosmic web that are not
mass dependent and seem to be stronger once the kinematic constraints
are imposed on the GS pairs. There is a clear anti-alignment between
the third eigenvector and the orbital angular momentum vector, meaning
that this vector is perpendicular to filaments and the sheets,  We
also found that the vector joining the LG halos are aligned with the
third eigenvector. This means that he pair is aligned with the filaments and
lies on the sheets and its motion is done along these directions.

@@

These alignments for the LG pairs could be in contradiction with
recent findings \citep{2014MNRAS.443.1274L} that report a universal
trend where the eigenvector $\hat{e}_{3}$ marks the infall direction
for substructures. For the Milky Way its satellites are located at
high galactic latitudes, almost perpendicular to the vector pointing towards
the Andromeda Galaxy, which is the direction that we find aligned with
$\hat{e}_3$.

If the alignment we find in this paper holds, this would imply that
infall in the case of the Milky Way is perpendicular to $\hat{e}_3$,
in contradiction to the universal principle of
\citep{2014MNRAS.443.1274L}. If the universal accretion alignment
holds, that would imply that that the Andromeda galaxy is located
perpendicular to $\hat{e}_3$, in contradiction with the strong
alignment found in this paper. It would be desirable to have a
measurement of the cosmic web in the Local Universe to disentangle
this potential contradiction between different alignments and
understading the detailed properties of the LG in an explicit
cosmological context.

\section*{Acknowledgements}
JEFR was supported by a FAPA grant by Vicerrector\'ia de
Investigaciones at Universidad de los Andes in Bogot\'a, Colombia.
REG was supported by Proyecto Financiamiento Basal PFB-06 'Centro de
Astronomia y Tecnologias Afines' and Proyecto Comit\'e Mixto ESO
3312-013-82. 
The Geryon cluster at the Centro de Astro-Ingenieria UC was
extensively used for the calculations performed in this paper. The
Anillo ACT-86, FONDEQUIP AIC-57, and QUIMAL 130008 provided funding
for several improvements to the Geryon cluster.
